Coherent optical association of a single molecule -- Supplemental material

### 2020-11-24 imgs/raman_spectroscopy_raman_beampath.tex
Compact figure

\begin{tikzpicture}
  \coordinate (Raman Input) at (2, 0);
  \coordinate (Raman Output) at (0, 2);
  \coordinate (DP PBS) at (0, 0);
  \coordinate (Wavemeter) at (0, -2);
  \coordinate (DP AOM) at (-2, 0);
  \coordinate (DP lens) at (-4.5, 0);
  \coordinate (DP M1) at (-6, 0);
  \coordinate (DP QWP) at (-6, 1.5);
  \coordinate (DP M2) at (-6 - 0.4, 2.5 + 0.05);
  \coordinate (SP QWP) at (-6, 3.5);
  \coordinate (SP IM1) at (-6, 5);
  \coordinate (SP lens) at (-7.5, 5);
  \coordinate (SP PBS) at (-9, 5);
  \coordinate (SP IM2) at (-11.5, 5);
  \coordinate (SP AOM) at (-11.5, 3.3);
  \coordinate (SP M1) at (-11.5, 0);
  \coordinate (SP M2) at (-9, 0);
  \coordinate (SP HWP) at (-9, 1.7);

  % Input
  \node[red,above] at (Raman Input) {\large\textbf{From Laser}};
  \draw[red,line width=1.6,mid arrow] (Raman Input) -- (DP PBS);
  % Wavemeter
  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, -1)$);
  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, -1)$) -- (Wavemeter);
  \node[red,below] at (Wavemeter) {\large\textbf{To wavemeter}};
  % Between PBS and DP AOM
  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
  \begin{scope}
    % Clip off one arrow
    \clip ($(DP AOM) + (0.77, 0)$) rectangle ($(DP AOM) + (0, 1)$);
    \draw[blue,line width=1.6,mid arrow2] (DP AOM) -- (DP PBS);
  \end{scope}
  \begin{scope}
    % Redraw the clipped line
    \clip (DP PBS) rectangle ($(DP AOM) + (0, 1)$);
    \draw[blue,line width=1.6] (DP AOM) -- (DP PBS);
  \end{scope}
  % Output
  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
  \begin{scope}
    \clip (DP PBS) rectangle (-1, 3);
    \draw[blue,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
    \draw[blue,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
  \end{scope}
  \node[red] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
  \begin{scope}
    \clip ($(Raman Output) + (-2, 0.3)$) rectangle ($(Raman Output) + (2, 1.5)$);
    \node[blue] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
  \end{scope}
  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP M1);
  \draw[blue,line width=1.6,mid arrow2] (DP AOM) --
  node[above,pos=0.34,rotate=-5] {\small $\approx\!+345~\mathrm{MHz}$} ($(DP M1) + (-0.3, 0.3)$);
  \draw[blue,line width=1.6,mid arrow2] ($(DP M1) + (-0.3, 0.3)$) -- (DP M2);
  \draw[red,line width=1.6,mid arrow2] (DP M1) -- (SP IM1);
  \draw[red,line width=1.6,mid arrow2] (SP lens) -- (SP IM1);
  \draw[red,line width=1.6] (SP lens) -- (SP PBS);
  \draw[red,line width=1.6] (SP PBS) -- ($(SP PBS) + (-1, 0)$);
  \draw[red,line width=1.6,mid arrow] ($(SP PBS) + (-1, 0)$) -- (SP IM2);
  \draw[red,line width=1.6] (SP IM2) -- (SP AOM);
  \draw[red,line width=1.6,mid arrow] (SP AOM) --
  node[above,rotate=86,pos=0.45] {\small $-80~\mathrm{MHz}$} ($(SP M1) + (-0.2, 0.2)$);
  \draw[red,line width=1.6,mid arrow] ($(SP M1) + (-0.2, 0.2)$) -- (SP M2);
  \draw[red,line width=1.6,mid arrow] (SP M2) -- (SP PBS);
  % Input PBS
  \drawpbs{(DP PBS)}{0.7}{0}
  \node[blue!40!cyan,below right] at ($(DP PBS) + (0.7, -0.7)$) {\large PBS 1};
  % DP AOM
  \drawaom{(DP AOM)}{1}{0.5}{90}
  \node[rotate=-90] at (DP AOM) {\large DP AOM};
  % DP Lens
  \drawlens{(DP lens)}{1}{90}
  \node[blue!80!cyan,below] at ($(DP lens) + (0, -1)$-4.5, -1) {\large L1};
  \drawmirror{(DP M1)}{0.9}{-45}
  % DP QWP
  \drawwaveplate{(DP QWP)}{1}{0}
  \node[blue!80!black,right] at ($(DP QWP) + (0.9, 0)$) {\large $\lambda/4$};
  \drawmirror{(DP M2)}{0.3}{3.8}
  % Post DP QWP
  \drawwaveplate{(SP QWP)}{1}{0}
  \node[blue!80!black,right] at ($(SP QWP) + (0.9, 0)$) {\large $\lambda/4$};
  \drawmirror{(SP IM1)}{0.9}{-45}
  % Post DP Lens
  \drawlens{(SP lens)}{1}{90}
  \node[blue!80!cyan,above] at ($(SP lens) + (0, 1)$) {\large L2};
  % SP PBS
  \drawpbs{(SP PBS)}{0.7}{0}
  \node[blue!40!cyan,above] at ($(SP PBS) + (0, 0.7)$) {\large PBS 2};
  \drawmirror{(SP IM2)}{0.9}{45}
  % SP AOM
  \drawaom{(SP AOM)}{1}{0.5}{0}
  \node at (SP AOM) {\large SP AOM};
  \drawmirror{(SP M1)}{0.9}{-45}
  \drawmirror{(SP M2)}{0.9}{45}
  % SP HWP
  \drawwaveplate{(SP HWP)}{1}{0}
  \node[blue!80!black,left] at ($(SP HWP) + (-0.9, 0)$) {\large $\lambda/2$};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \coordinate (Raman Input) at (2, 0);
  \coordinate (Raman Output) at (0, 2);
  \coordinate (DP PBS) at (0, 0);
  \coordinate (Wavemeter) at (0, -2);
  \coordinate (DP AOM) at (-1.7, 0);
  \coordinate (DP lens) at (-4.2, 0);
  \coordinate (DP M1) at (-5.2, 0);
  \coordinate (DP QWP) at (-5.2, 1.4);
  \coordinate (DP M2) at (-5.2 - 0.4, 2.0 + 0.05);
  \coordinate (SP QWP) at (-5.2, 2.9);
  \coordinate (SP IM1) at (-5.2, 4);
  \coordinate (SP lens) at (-6.5, 4);
  \coordinate (SP PBS) at (-7.5, 4);
  \coordinate (SP IM2) at (-10, 4);
  \coordinate (SP AOM) at (-10, 2.7);
  \coordinate (SP M1) at (-10, 0);
  \coordinate (SP M2) at (-7.5, 0);
  \coordinate (SP HWP) at (-7.5, 1.7);

  % Input
  \node[red,above] at (Raman Input) {\large\textbf{From Laser}};
  \draw[red,line width=1.6,mid arrow] (Raman Input) -- (DP PBS);
  % Wavemeter
  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, -1)$);
  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, -1)$) -- (Wavemeter);
  \node[red,below] at (Wavemeter) {\large\textbf{To wavemeter}};
  % Between PBS and DP AOM
  \draw[red,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
  \draw[red,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
  \begin{scope}
    % Clip off one arrow
    \clip ($(DP AOM) + (0.9, 0)$) rectangle ($(DP AOM) + (0, 1)$);
    \draw[blue,line width=1.6] ($(DP PBS) + (-1.2, 0)$) -- (DP AOM);
    \draw[blue,line width=1.6,mid arrow2] ($(DP PBS) + (-1.2, 0)$) -- (DP PBS);
  \end{scope}
  \begin{scope}
    % Redraw the clipped line
    \clip (DP PBS) rectangle ($(DP AOM) + (0, 1)$);
    \draw[blue,line width=1.6] (DP AOM) -- (DP PBS);
  \end{scope}
  % Output
  \draw[red,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
  \draw[red,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
  \begin{scope}
    \clip (DP PBS) rectangle (-1, 3);
    \draw[blue,line width=1.6] (DP PBS) -- ($(DP PBS) + (0, 1)$);
    \draw[blue,line width=1.6,mid arrow] ($(DP PBS) + (0, 1)$) -- (Raman Output);
  \end{scope}
  \node[red] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
  \begin{scope}
    \clip ($(Raman Output) + (-2, 0.3)$) rectangle ($(Raman Output) + (2, 1.5)$);
    \node[blue] at ($(Raman Output) + (0, 0.3)$) {\large\textbf{To Experiment}};
  \end{scope}
  \draw[red,line width=1.6,mid arrow2] (DP AOM) -- (DP M1);
  \draw[blue,line width=1.6,mid arrow2] (DP AOM) --
  node[above,pos=0.38,rotate=-6] {\small $\approx\!+345~\mathrm{MHz}$} ($(DP M1) + (-0.3, 0.3)$);
  \draw[blue,line width=1.6,mid arrow2] ($(DP M1) + (-0.3, 0.3)$) -- (DP M2);
  \draw[red,line width=1.6,mid arrow2] (DP M1) -- (SP IM1);
  \draw[red,line width=1.6,mid arrow2] (SP lens) -- (SP IM1);
  \draw[red,line width=1.6] (SP lens) -- (SP PBS);
  \draw[red,line width=1.6] (SP PBS) -- ($(SP PBS) + (-1, 0)$);
  \draw[red,line width=1.6,mid arrow] ($(SP PBS) + (-1, 0)$) -- (SP IM2);
  \draw[red,line width=1.6] (SP IM2) -- (SP AOM);
  \draw[red,line width=1.6,mid arrow] (SP AOM) --
  node[above,rotate=86,pos=0.5] {\small $-80~\mathrm{MHz}$} ($(SP M1) + (-0.2, 0.2)$);
  \draw[red,line width=1.6,mid arrow] ($(SP M1) + (-0.2, 0.2)$) -- (SP M2);
  \draw[red,line width=1.6,mid arrow] (SP M2) -- (SP PBS);
  % Input PBS
  \drawpbs{(DP PBS)}{0.7}{0}
  \node[blue!40!cyan,below right] at ($(DP PBS) + (0.7, -0.7)$) {\large PBS 1};
  % DP AOM
  \drawaom{(DP AOM)}{1}{0.5}{90}
  \node[rotate=-90] at (DP AOM) {\large DP AOM};
  % DP Lens
  \drawlens{(DP lens)}{1}{90}
  \node[blue!80!cyan,below] at ($(DP lens) + (0, -1)$-4.5, -1) {\large L1};
  \drawmirror{(DP M1)}{0.9}{-45}
  % DP QWP
  \drawwaveplate{(DP QWP)}{1}{0}
  \node[blue!80!black,right] at ($(DP QWP) + (0.9, 0)$) {\large $\lambda/4$};
  \drawmirror{(DP M2)}{0.3}{3.8}
  % Post DP QWP
  \drawwaveplate{(SP QWP)}{1}{0}
  \node[blue!80!black,right] at ($(SP QWP) + (0.9, 0)$) {\large $\lambda/4$};
  \drawmirror{(SP IM1)}{0.9}{-45}
  % Post DP Lens
  \drawlens{(SP lens)}{1}{90}
  \node[blue!80!cyan,above] at ($(SP lens) + (0, 1)$) {\large L2};
  % SP PBS
  \drawpbs{(SP PBS)}{0.7}{0}
  \node[blue!40!cyan,above] at ($(SP PBS) + (0, 0.7)$) {\large PBS 2};
  \drawmirror{(SP IM2)}{0.9}{45}
  % SP AOM
  \drawaom{(SP AOM)}{1}{0.5}{0}
  \node at (SP AOM) {\large SP AOM};
  \drawmirror{(SP M1)}{0.9}{-45}
  \drawmirror{(SP M2)}{0.9}{45}
  % SP HWP
  \drawwaveplate{(SP HWP)}{1}{0}
  \node[blue!80!black,left] at ($(SP HWP) + (-0.9, 0)$) {\large $\lambda/2$};
\end{tikzpicture}
